### 2010-12-05 docs/tex/result.tex
New image update.

\section{Initial configuration with two prey species}
% Put the table here
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 108 
  														& \multicolumn{2}{|c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  & 108 
  					 									& \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 2 prey species}
\label{tab:config-table-2-prey}
\end{table}

@@

Prey demise age has been kept to 2000 iterations while predator demise age is set to 2500. But later in the following results predator demise age has been increased to 5000 iterations. Predators in this simulation generates selection pressure for the evolution of mimicry. So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid. But with the current rate of demise for predator we were able to create successful mimetic population of prey species as we will see in the analysis in the following results.

@@

By closely observing the graph we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species. At around time 1000 the prey population starts reproducing as the population increases. At around the same time different other species of prey population gets to be born with mutated CA patterns. Over time the population of CA Rule 110 dominates the population as most predators recognizes it as unpalatable. And similarly a population of CA Rule 110 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 30 (Time: 5000 approx.) which was initially considered as a set of palatable species.

@@

As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 33 rings at the end of 10000 iterations. We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented. For example if we observe the set of pattern genotype with very different phenotype in Table \ref{tab:diff-in-pattern}.

>>>>

\section{Initial configuration with two prey species}
% Put the table here
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} & 108 
  														& \multicolumn{2}{|c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  & 108 
  					 									& \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{1000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{2400} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 2 prey species}
\label{tab:config-table-2-prey}
\end{table}

@@

Prey demise age has been kept to 2000 iterations while predator demise age is set to 2400. But later in the following results predator demise age has been increased to 5000 iterations. Predators in this simulation generates selection pressure for the evolution of mimicry. So the longer a predator is present in the simulation it will be making intelligent decisions in term of selecting which prey species to consume and which one to avoid. But with the current rate of demise for predator we were able to create successful mimetic population of prey species as we will see in the analysis in the following results.

@@

By closely observing the graph we could see the population of two species have started dropping at around time 500 when the initial predator population reaches this maturity for consuming prey species. At around time 1000 the prey population starts reproducing as the population increases. At around the same time different other species of prey population gets to be born with mutated CA patterns. Over time the population of CA Rule 30 dominates the population as most predators recognizes it as unpalatable. And similarly a population of CA Rule 30 or within the same ring of palatable species starts rising, while at one point overlaps the population of CA Rule 110 (Time: 5000 approx.) which was initially considered as a set of palatable species.

@@

As it can be observed from Figure \ref{fig:ringSize10k-2Prey} the number of rings in this simulation makes a slow increase from 2 at the initial configuration to 26 rings at the end of 10000 iterations. We can observe that a small change in CA genetic representation can have a very large effect in terms of the phenotype of the pattern with which the prey is represented. For example if we observe the set of pattern genotype with very different phenotype in Table \ref{tab:diff-in-pattern}.
